A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-29 ICLP Paper/samplepaper.tex
conclusions updated

\section{Conclusions}\label{sec:conclusions}
In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.

>>>>

\section{Conclusions}\label{sec:conclusions}
%
Our work develops multi-shot ASP modulo DL methods for JSP solving,
based on problem decomposition into balanced time windows that respect the operation
precedence within jobs and successive makespan optimization while extending
partial schedules to a global solution.
We demonstrate that splitting highly complex JSP instances into
balanced portions, for which partial schedules of good quality can be reliably
found within tight runtime limits, leads to significantly better global solutions
than obtainable with single-shot ASP modulo DL optimization in similar runtime.
Related works taking advantage of single- \citep{abjoossctowa21a}
and multi-shot solving \citep{francescutto2021solving} by
\clingodl to tackle real-world scheduling problems evaluate threshold values
on DL variables and perform optimization by means of common 
\lstinline{#minimize} statements of \clingo rather than minimizing the
value of a DL variable like \lstinline{makespan} in Listing~\ref{prg:encoding}.
Applying a similar approach can be advantageous in our future work as it may
potentially improve computational efficiency as well as solution quality further
and is even a necessity to switch from the makespan as optimization objective to tardiness
w.r.t.\ deadlines, which are crucial in many application areas.
Moreover, we aim to generalize our methods further, e.g.,
by considering flexible machine allocations and varying processing times,
and scale them up to large-scale instances with an order of magnitude more
operations than in synthetic benchmarks.
%
% In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.
